% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Vinoth Kumar Shanmugam}{Februray 07, 1989}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:vin.omega@gmail.com}{vin.omega\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller
{+}1.6787073805\sbull
Atlanta\sbull
Georgia

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Experienced full stack developer who is passionate about building high quality apps with modern web technologies.Strong organizational, management and communication skills, target-oriented, self-motivated, self-starter and a team player while being an effective individual contributor.}
\\

Graduated from crescent engineering college, India (2006-2010) at age of 21 and started my carier with iGate Global Solutions which is now part of Capgemini.

I started my earlie carier as a Java programer working with Spring, Struts, IBM WebSphere Portlet and JSP. Around early 2014 I found my way into hybrid mobile app development since then I have been working as a full stack developer focusing more on advanced java scripts, objective C, Java, OSGI, micro services and more.

Recently I have been an javascript enthusiast and want to be active part of the open source movement. 
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\textnormal{SmartOutage, GE Power}}
  {\textsc{Atlanta, Georgia}} {
  \headedsubsection
    {Software Engineer}
    {Feb \apo14 -- present}
    {\bodytext{}}
  \headedsubsection
    {Team Lead}
    {Apr \apo15 -- present}
    {\bodytext{}}
}

\headedsection
  {\textnormal{My Fleet, GE Power}}
  {\textsc{Atlanta, Georgia}} {
  \headedsubsection
    {Software Engineer}
    {Oct \apo13 -- Jan \apo13}
    {\bodytext{}}
}

\headedsection
  {\textnormal{M&D Catalog, GE Power}}
  {\textsc{Chennai, India}} {
  \headedsubsection
    {Software Engineer}
    {May \apo13 -- Sept \apo13}
    {\bodytext{}}
}

\headedsection
  {\textnormal{Digital Catalog, GE Oil&Gas}}
  {\textsc{Chennai, India}} {
  \headedsubsection
    {Software Engineer}
    {Oct \apo12 -- Apr \apo13}
    {\bodytext{}}
}

\headedsection
  {\textnormal{Custmer Database, TNT}}
  {\textsc{Chennai, India}} {
  \headedsubsection
    {Software Engineer}
    {Jan \apo10 -- Sept \apo12}
    {\bodytext{}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Leading and recruiting for team(s) of software workers.  Big fan of Agile methodologies and continuous delivery and functional programming.  Enjoys writing Java/\nsp Java script/\nsp.  Solid knowledge of web technologies. Knowledge to architect and implement a system from scratch.  Strong skills on Project setup. Linux administration skills (e.g.\ Bash scripting, Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}, ElasticSearch).  Well experienced with Docker and DevOps model.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {\href{https://en.wikipedia.org/wiki/Tamil_language}{Tamil} \emph{(mother tongue)}, English \emph{(full professional proficiency)}.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {history, music (from classical to metal), \acr{NLP}, open source, philosophy, travel and cooking.}

\end{document}
